There once was a grid at ol' Carkeek

### 2016-03-16 Manuscript/carkeek_grid.tex
add methods subsections

%-----------------------------------METHODS-------------------------------------
\section*{Methods}
We use the general framework outlined by Shelton et al (CITE).
That study outlined the structure for estimation of the proportional biomass of a taxon ($B_i$) given the proportional counts of sequences recovered from a parallel sequencing run ($Z_i$).

>>>>

%-----------------------------------METHODS-------------------------------------
\section*{Methods}
\subsection*{Environmental Sampling}
We collected samples from 8 points along three parallel transects, separated by 1000m.
The first sample was collected over a lower-intertidal patch of \textit{Zostera marina}, with samples taken at 75, 125, 250, 500, 1000, 2000, and 4000 meters along the transect.

\subsection*{Laboratory Methods}

\subsection*{Data Preparation (Bioinformatics)}

\subsection*{Model Formulation}
We use the general framework outlined by Shelton et al (CITE).
That study outlined the structure for estimation of the proportional biomass of a taxon ($B_i$) given the proportional counts of sequences recovered from a parallel sequencing run ($Z_i$).
